04_DESeq_sexes

### 2019-05-24 analysis/04_DESeq2_sexes.Rmd
now with separate functions for table and plot yea

```{r totalDEGs, eval = T}
#create list of groups for deseq contrasts
group1 <- levels(a.colData$treatment)
group2 <- group1

a <- plottotalDEGs(dds.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(dds.female_pituitary, "female pituitary")
c <- plottotalDEGs(dds.female_gonad, "female gonad")
d <- plottotalDEGs(dds.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(dds.male_pituitary, "male pituitary")
f <- plottotalDEGs(dds.male_gondad, "male gonad")
```

>>>>

```{r returntotalDEGs, eval = T}
DEGs.female_hypothalamus <- returntotalDEGs(dds.female_hypothalamus)
DEGs.female_pituitary <- returntotalDEGs(dds.female_pituitary)
DEGs.female_gonad <- returntotalDEGs(dds.female_gonad)
DEGs.male_hypothalamus <- returntotalDEGs(dds.male_hypothalamus)
DEGss.male_pituitary <- returntotalDEGs(dds.male_pituitary)
DEGs.male_gondad <- returntotalDEGs(dds.male_gondad)
```

```{r plotDEGs, eval = T}
a <- plottotalDEGs(DEGs.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(DEGs.female_pituitary, "female pituitary")
c <- plottotalDEGs(DEGs.female_gonad, "female gonad")
d <- plottotalDEGs(DEGs.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(DEGss.male_pituitary, "male pituitary")
f <- plottotalDEGs(DEGs.male_gondad, "male gonad")
```
